---
title: "Assignment 2 - Data Analysis 2 and Coding with R"
author: "David Utassy"
date: "01/01/2021"
output: 
  #html_document
  pdf_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this project I address the question, how to predict from some measurable variables whether someone has heart disease. This is an important question as according to the World Health Organization, cardiovascular diseases are the leading cause of death globally. Of course, this topic requires broad knowledge on the topic. To get familiar with the problem I recommend [this article](https://www.kaggle.com/carlosdg/a-detail-description-of-the-heart-disease-dataset), which describes the theory in an understandable way. 


# Data

This dataset is hosted on Kaggle (Heart Disease Dataset)[https://www.kaggle.com/johnsmith88/heart-disease-dataset], it is from 1988 and consists of four databases: Cleveland, Hungary, Switzerland, and Long each. The original data source is the [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/Heart+Disease), which contains 76 attributes, but all published experiments refer to using a subset of 14 of them, so as mine.  

In the dataset, every row is a person with the given parameters in each column. The number of the observations is 1025 originally, which will decrease to 1000 after omitting some with missing values. This dataset was pretty clean already, only a few modifications were needed to make the analysis more convenient. 

The most challenging part of this project is to understand somehow the variables I have. In order to get the reader somewhat familiar with them, I introduce them in a few sentences in an easy to understand form. For further details, I recommend the previously mentioned online sources.

1. Target: (binary) whether the patient has heart disease or not (originally 0: yes, 1: no) but I made a modification, therefore 0: no, 1: yes
2. Age: (quantitative) the age of the patient
3. Gender: (binary) The gender of the patient (0:female, 1: male)
4. Chest pain type (qualitative)
    - Value 0: asymptomatic (no symptoms)
    - Value 1: atypical angina
    - Value 2: pain without relation to angina
    - Value 3: typical angina
5. Resting blood pressure in mm Hg (qualitative)
6. Serum cholesterol in mg/dl: The level of cholesterol in the blood 
7. Fasting blood sugar > 120 mg/dl: (binary) Whether the level of blood sugar is under or above the threshold (0: under, 1:above) 
8. Resting electrocardiographic results (qualitative)
    - Value 0: probable left ventricular hypertrophy
    - Value 1: normal
    - Value 2: abnormalities in the T wave or ST segment
9. Maximum heart rate achieved (qualitative)
10. Exercise-induced angina: (binary) whether pain occurred during exercise (0: no, 1: yes)
11. Oldpeak: (quantitative) Decrease of the ST segment during exercise according to the same one on rest. (0 is optimal)
12. The slope of the peak exercise ST segment: (qualitative) the slope of a specified line segment on the ECG
    - Value 0: descending
    - Value 1: flat
    - Value 2: ascending
13. Number of major vessels (0-3) colored by fluoroscopy: (qualitative, ordered) Number of narrow vessels, ideally should be 0.
14. Results of the blood flow observed via the radioactive dye
    - Value 1: fixed defect (no blood flow in some part of the heart)
    - Value 2: normal blood flow
    - Value 3: reversible defect (a blood flow is observed but it is not normal)


```{r include=FALSE}
# Clear memory
rm(list=ls())

# Packages to use
library(tidyverse)
# For scaling ggplots
require(scales)
# Estimate piecewise linear splines
#install.packages("lspline")
library(lspline)
# Estimate robust SE
#install.packages("estimatr")
library(estimatr)
# Compare models with robust SE
#install.packages("texreg")
library(texreg)
# For different themes
#install.packages("ggthemes")
library(ggthemes)

library(ggplot2)
library("ggpubr")
theme_set(
  theme_bw() +
    theme(legend.position = "top")
  )
library(moments)
library(kableExtra)


library(mfx)
library(margins)
library(pscl)
library(modelsummary)
library(stargazer)

# Call the data from github
my_url <- "https://raw.githubusercontent.com/utassydv/analysis_heart_disease/main/data/raw/heart.csv"
df <- read_csv( my_url )

#managing some problems in the dataset
#removing observations with ca=4, as it means missing value
df <- subset(df, ca!=4) #18 removed

#removing observations with thal=0, as it means missing value
df <- subset(df, thal!=0) #7removed

#currently in the target column, we have an inverse logic heart disease(0:yes, 1:no), let's fix this!
df$heart_dis[df$target == 0] <- 1
df$heart_dis[df$target == 1] <- 0
df$heart_dis <- as.numeric(df$heart_dis)
df$target <- NULL

# Quick check on all HISTOGRAMS
df %>%
  keep(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) +
  facet_wrap(~key, scales = "free") +
  geom_histogram()+
  theme_wsj() + 
  scale_fill_wsj()

# Some distributions are skewed with a right tail. With those variables it worths to make a log transformation.
df <- df %>% mutate( ln_oldpeak = log( oldpeak ),
                    ln_trestbps = log( trestbps ),
                    ln_chol = log( chol ) )

p1<- ggplot( df , aes( x = trestbps ) ) +
    geom_histogram( aes(y = ..density..) , alpha = 1, binwidth = 10, color = 'black', fill = 'white') +
    geom_density( aes(y = ..density..) , alpha = .2 , bw = 10, color = 'black', fill="#FF6666") +
    labs(x='Resting blood pressure (mm Hg)',y='Density')
p2<- ggplot( df , aes( x = ln_trestbps ) ) +
    geom_histogram( aes(y = ..density..) , alpha = 1, binwidth = 0.06, color = 'black', fill = 'white') +
    geom_density( aes(y = ..density..) , alpha = .2 , bw = 0.06, color = 'black', fill="#56B4E9") +
    labs(x='Resting blood pressure (mm Hg) on ln scale',y='Density')

p3<- ggplot( df , aes( x = chol ) ) +
    geom_histogram( aes(y = ..density..) , alpha = 1, binwidth = 20, color = 'black', fill = 'white') +
    geom_density( aes(y = ..density..) , alpha = .2 , bw = 20, color = 'black', fill="#FF6666") +
    labs(x='Serum cholestoral (mg/dl)',y='Density')
p4<- ggplot( df , aes( x = ln_chol ) ) +
    geom_histogram( aes(y = ..density..) , alpha = 1, binwidth = 0.1, color = 'black', fill = 'white') +
    geom_density( aes(y = ..density..) , alpha = .2 , bw = 0.1, color = 'black', fill="#56B4E9") +
    labs(x='Serum cholestoral (mg/dl) on ln scale',y='Density')

create_summary_table <-function (df, name, variable_name){
  row <- df %>% summarise(
  variable = name,
  mean     = mean(variable_name),
  median   = median(variable_name),
  std      = sd(variable_name),
  min      = min(variable_name),
  max      = max(variable_name),
  skew     = skewness(variable_name) )
  return(row)
}

heart_dis_sum <- create_summary_table(df, 'Heart disease (0: no, 1: yes)', df$heart_dis)
age_sum <- create_summary_table(df, 'Age', df$age)
sex_sum <- create_summary_table(df, 'Gender (0:female, 1:male)', df$sex)
trestbps_sum <- create_summary_table(df, 'Resting blood pressure (mm Hg)', df$trestbps)
chol_sum <- create_summary_table(df, 'Cholesterol level (mg/dl)', df$chol)
fbs_sum <- create_summary_table(df, 'Fasting blood sugar > 120 mg/dl (0: under, 1:above)', df$fbs)
thalach_sum <- create_summary_table(df, 'Maxium heart rate during the stress test', df$thalach)
exang_sum <- create_summary_table(df, 'Exercise-induced angina (0: no, 1: yes)', df$exang)
oldpeak_sum <- create_summary_table(df, 'Oldpeek', df$oldpeak)
ca_sum <- create_summary_table(df, 'Number of main blood vessels ', df$ca)


df_summary <- heart_dis_sum %>% 
          add_row( age_sum ) %>% 
          add_row( sex_sum ) %>% 
          add_row( trestbps_sum ) %>% 
          add_row( chol_sum ) %>% 
          add_row( fbs_sum ) %>% 
          add_row( thalach_sum ) %>% 
          add_row( exang_sum ) %>% 
          add_row( oldpeak_sum ) %>% 
          add_row( ca_sum ) 

w_dir <- "/Users/utassydv/Documents/workspaces/CEU/my_repos/analysis_heart_disease"

source(paste0(w_dir,'/codes/sum_stat.R'))
```

```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
kbl(df_summary, digits = 2) %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "center")
```


In order to get to know my variables, I have made some basics histograms. From those, it was visible that some variables might need a log transformation. In the appendix, we can see the result of some possible transformations, but in the end, I decided to stay with the original scales as the modifications probably would not pay off.  

The table above contains the summary statistics of the variables I used in the analysis. To highlight some patterns in our data, the mean of the presence of heart disease is almost 50%, which could be good for prediction, however, 70% of the observations are male, which is not representing the population well. The age variable also shows that the sample is not really representing a whole population, but probably a subset of people who has to do something with cardiovascular problems. The other variables are more like medical terms, therefore I would not go into detailed preconceptions. 

```{r include=FALSE}
create_plot <- function(column, name){
  plot <- ggplot(data = df, aes(x=column, y=heart_dis)) +
  geom_point(aes(x = column, y = heart_dis), color="red", shape = 16, alpha=0.8, show.legend=F, na.rm=TRUE)  +
  geom_smooth(method="loess", color="blue") +
  labs(x = name,y = "Heart disease (0: no, 1: yes)") +
  theme(text = element_text(size=20))
  
  return(plot)
}

p_age <- create_plot(df$age, "Age")
p_male <- create_plot(df$sex, "Male")
p_cp <- create_plot(df$cp, "Chest pain type")
p_trestbps <- create_plot(df$trestbps, "Resting blood pressure (mm Hg)")
p_chol <- create_plot(df$chol, "Serum Cholesterol")
p_restecg <- create_plot(df$restecg, "Resting electrocardiographic results")
p_thalach <- create_plot(df$thalach, "Maximum heart rate achieved")
p_exang <- create_plot(df$exang, "Exercise induced angina (1 = yes; 0 = no)")
p_oldpeak <- create_plot(df$oldpeak, "ST depression induced by exercise relative to rest")
p_slope <- create_plot(df$slope, "The slope of the peak exercise ST segment")
p_ca <- create_plot(df$ca, "Number of major vessels (0-3) colored by flourosopy")
p_thal <- create_plot(df$thal, "1 = fixed defect; 2 = normal; 3 = reversable defect")
```

# Model
In order to create a proper model, it worth to visualize the association between variables. In the appendix, I plotted all the meaningful associations.

```{r fig 2, fig.width=18,fig.height=5,  echo = FALSE , results = 'asis', warning = FALSE, message = FALSE }
ggarrange(p_male, 
          p_oldpeak,
          nrow = 1, ncol = 2 )
```

On the plots above we can see two plots from the ones mentioned before. It can be easily seen that men have heart disease more likely than women and that ST depression induced by exercise has a positive correlation with heart disease as well. These are just two variables out of 13 but in the appendix, the association of other variables with the presence of heart disease can be observed. It turns out, that almost all of the provided variables have some correlation with the presence of heart disease. Therefore I will try to use all of them in an LPM, logit, and probit model.




```{r include=FALSE}
####
# LPM MODELS

lpm1 <- lm( heart_dis ~ sex , data = df )
summary( lpm1, vcov=sandwich )

# Get the predicted values
df$pred1 <- predict( lpm1 )

# Compare smoking with predicted values and real outcomes
table(df$pred1, df$heart_dis)
table(df$heart_dis, df$sex)


lpm2 <- lm( heart_dis ~ sex + lspline(age,c(52,61)) , data = df )
summary( lpm2 , vcov = sandwich )


# Creating a model formula, that contains all of our variables
model_formula <- formula( heart_dis ~ sex + lspline(age,c(52,61)) + as.factor(cp) + lspline(trestbps,c(115,130)) + lspline(chol,c(210,270,430)) +fbs + as.factor(restecg) +
           lspline(thalach,c(140)) + exang +  lspline(oldpeak,c(4)) + as.factor(slope) + ca + as.factor(thal))

lpm <- lm( model_formula,  data = df )

summary( lpm , vcov=sandwich )

stargazer(list(lpm1, lpm2, lpm), digits=3, out=paste(w_dir,"/out/lpm_models.html",sep=""))

# predicted probabilities
df$pred_lpm <- predict( lpm )
# Make a descriptive summary of the predictions!
summary( df$pred_lpm )

# Show the predicted probabilities' distribution (ggplot)
ggplot( df , aes( x = pred_lpm ) ) +
  geom_histogram( fill = 'navyblue' , color = 'grey90')
  

# We are interested in the top 1% and bottom 1% characteristics!
#   Is there any significant difference?

# Create bins which categorize the predicted values between 1-100
df <- df %>% 
  mutate( q100_pred_lpm = ntile(pred_lpm, 100) )

# Make a summary statistics, using sum_stat for the bottom (q100_pred_lpm==1) 
#   and top 1% (q100_pred_lpm==100), using stats = c('mean','median','sd')
#   and variables c('smoking','ever_smoked','female','age','eduyears','income10','bmi','exerc')
#   use the num_obs = F input for sum_stat

# Top 1%, ones who probably has heart disease 
t1 <- sum_stat( subset( df , q100_pred_lpm==100 ) , 
                c('age','sex','cp','trestbps','chol','fbs','restecg','thalach','exang','oldpeak','slope','thal','ca'),
                c('mean','median','sd'),
                num_obs = F )
t1

# Bottom 1%, ones who probably does not have heart disease 
b1 <- sum_stat( subset( df , q100_pred_lpm==1 ) , 
                c('age','sex','cp','trestbps','chol','fbs','restecg','thalach','exang','oldpeak','slope','thal','ca'),
                c('mean','median','sd'),
                num_obs = F )
b1



####
#LOGIT AND PROBIT MODELS
#

#LOGIT
# logit coefficients:
logit <- glm( model_formula , data=df, family=binomial(link="logit") )
summary(logit)
glance(logit)

# predicted probabilities 
df$pred_logit <- predict.glm(logit, type="response")
summary(df$pred_logit)

# Calculate logit marginal differences
logit_marg <- logitmfx( model_formula, data=df, atmean=FALSE, robust = T)
print(logit_marg)


##PROBIT
# Probit coefficients: replicate logit, but now use 'probit'
probit <- glm( model_formula , data = df , family=binomial(link="probit") )
summary(probit)

# predicted probabilities 
df$pred_probit<- predict.glm( probit , type = "response" )
summary( df$pred_probit )

# probit marginal differences
probit_marg <- probitmfx(  model_formula, data=df, atmean=FALSE, robust = T)
print( probit_marg )

# Comparing predicted probabilities of logit and probit to LPM
df$pred_lpm <- predict(lpm)
ggplot(data = df) +
  geom_point(aes(x=pred_lpm, y=pred_probit, color="Probit"), size=1,  shape=16) +
  geom_point(aes(x=pred_lpm, y=pred_logit,  color="Logit"), size=1,  shape=16) +
  geom_line(aes(x=pred_lpm, y=pred_lpm,    color="45 degree line"), size=1) +
  labs(x = "Predicted probability of having heart disease (LPM)", y="Predicted probability")+
  scale_y_continuous(expand = c(0.00,0.0), limits = c(0,1), breaks = seq(0,1,0.1)) +
  scale_x_continuous(expand = c(0.00,0.0), limits = c(0,1), breaks = seq(0,1,0.1)) +
  scale_color_manual(name = "", values=c("green", "red","blue"))+
  theme(legend.position=c(0.55,0.08),
        legend.direction = "horizontal",
        legend.text = element_text(size = 4))

# Also can use stargazer...
stargazer(list(lpm, logit, probit), digits=3, out=paste(w_dir,"/out/T11_reg3_R.html",sep=""))

####
# 5. PART - GOODNESS OF FIT
#

# logit rich model
predict_lpm = ggplot(data = df,aes(x=pred_lpm)) + 
  geom_histogram(data=subset(df[df$heart_dis == 1, ]), 
                 aes(fill=as.factor(heart_dis), color=as.factor(heart_dis), y = (..count..)/sum(..count..)*100),
                 binwidth = 0.05, boundary=0, alpha=0.8) +
  geom_histogram(data=subset(df[df$heart_dis == 0, ]), 
                 aes(fill=as.factor(heart_dis), color=as.factor(heart_dis), y = (..count..)/sum(..count..)*100), 
                 binwidth = 0.05, boundary=0, alpha=0) +
  scale_fill_manual(name="", values=c("0" = "white", "1" = "red"),labels=c("Does not have heart disease","Has heart disease")) +
  scale_color_manual(name="", values=c("0" = "blue", "1" = "red"),labels=c("Does not have heart disease","Has heart disease")) +
  ylab("Percent") +
  xlab("Fitted values") +
  scale_x_continuous(expand=c(0.01,0.01) ,limits = c(-0.5,1.5), breaks = seq(0,1,0.2)) +
  scale_y_continuous(expand=c(0.00,0.00) ,limits = c(0,20), breaks = seq(0,20,4)) +
  theme(legend.position = c(0.7,0.8),
        legend.key.size = unit(x = 0.5, units = "cm"))

predict_logit = ggplot(data = df,aes(x=pred_logit)) + 
  geom_histogram(data=subset(df[df$heart_dis == 1, ]), 
                 aes(fill=as.factor(heart_dis), color=as.factor(heart_dis), y = (..count..)/sum(..count..)*100),
                 binwidth = 0.05, boundary=0, alpha=0.8) +
  geom_histogram(data=subset(df[df$heart_dis == 0, ]), 
                 aes(fill=as.factor(heart_dis), color=as.factor(heart_dis), y = (..count..)/sum(..count..)*100), 
                 binwidth = 0.05, boundary=0, alpha=0) +
  scale_fill_manual(name="", values=c("0" = "white", "1" = "red"),labels=c("Does not have heart disease","Has heart disease")) +
  scale_color_manual(name="", values=c("0" = "blue", "1" = "red"),labels=c("Does not have heart disease","Has heart disease")) +
  ylab("Percent") +
  xlab("Fitted values") +
  scale_x_continuous(expand=c(0.01,0.01) ,limits = c(0,1), breaks = seq(0,1,0.2)) +
  scale_y_continuous(expand=c(0.00,0.00) ,limits = c(0,20), breaks = seq(0,20,4)) +
  theme(legend.position = c(0.7,0.8),
        legend.key.size = unit(x = 0.5, units = "cm"))

#####
# Summary statistics on predicted probabilities:

source(paste0(w_dir,'/codes/sum_stat.R'))
hd <- sum_stat( subset( df , heart_dis == 1 ) , 
                c( "pred1","pred_lpm","pred_logit","pred_probit" ),
                c("mean","median","min","max","sd"),
                num_obs = F )

nhd <- sum_stat( subset( df , heart_dis == 0 ) , 
                c( "pred1","pred_lpm","pred_logit","pred_probit" ),
                c("mean","median","min","max","sd"),
                num_obs = F )

hd
nhd

###
# Bias and Calibration curve
#
# Lets use the logit model!
#
# Biased prediction? Calculate bias!
#   Hint: bias = mean(prediction) - mean(actual)
bias <- mean( df$pred_logit ) - mean(df$heart_dis)
# 

# Note dplyr:: is important to specify which package's 'select' is used!
actual_vs_predicted <- df %>%
  ungroup() %>% 
  dplyr::select(actual = heart_dis, 
                predicted = pred_logit) 
num_groups <- 10

calibration_d <- actual_vs_predicted %>%
  mutate(predicted_score_group = dplyr::ntile(predicted, num_groups))%>%
  group_by(predicted_score_group) %>%
  dplyr::summarise(mean_actual = mean(actual), 
                   mean_predicted = mean(predicted), 
                   num_obs = n())

ggplot( calibration_d,aes(x = mean_actual, y = mean_predicted)) +
  geom_point( color='red', size=1.5, alpha=0.8) +
  geom_line(  color='red', size=1  , alpha=0.8) +
  geom_abline( intercept = 0, slope = 1, color='blue') +
  labs( x = "Actual event probability", y = "Predicted event probability") +
  scale_x_continuous(expand = c(0.01,0.01), limits = c(0,1), breaks = seq(0,1,0.1)) +
  scale_y_continuous(expand = c(0.01,0.01), limits = c(0,1), breaks = seq(0,1,0.1))

###
# TO DO: create a function which creates a graphs!
# Inputs:
#   dataset, outcome, pred_prob_name, num_groups
# Output:
#   graph and calibration_d


##
# 7. PART - CONFUSION TABLES
#
# Handy for classification!
#   will learn more on DA3

# Create a new data_frame just for simplicity!
df2 <- data.frame(df$pred1, df$pred_lpm, df$pred_logit, df$pred_probit)

# Set the threshold value
threshold <- 0.5

# Decide for each observations and each prediction, if larger than the treshold value!
for (i in 1:nrow(df2)) {
  for (j in 1:ncol(df2)) {
    if (df2[i,j]>threshold) {df2[i,j]=1}
    else {df2[i,j]=0}
  }
}

# confusion matrix - does it seems similar?
for (j in 1:ncol(df2)){
  print(prop.table(table(df2[, j], df$heart_dis)))
}


```

In the experimenting phase, I have created different models to capture the data in my sample. In the appendix, one can see the summary table of three different LPM models.  At the bottom of that table, we can compare the three models with the R$^2$ attribute. According to that, it is clear, that we should go on with the model that has all the variables.


In order to handle nonlinearities, I used piecewise linear splines according to the already mentioned plots. Furthermore to handle quantitative variables I used them as a factor (which creates n-1 dummy variables in the model).

In order to get closer to possible prediction, we want our model to give the probability between 0 and 1 on the presence of heart disease in a patient. In our case with the LPM model, we are in trouble as it gives predictions under zero and above one as well.

```{r fig 0, fig.width=8,fig.height=3,  echo = FALSE , results = 'asis', warning = FALSE, message = FALSE}
predict_lpm
```

The solution is to use logit or probit model instead of LPM. This will predict only probabilities between 0 and 1. To be able to interpret the logit and probit models we should calculate the marginal differences as well. In the appendix, we can see the comparison of the LPM the Logit, and he Probit model.  At the bottom of the table, we can also compare them in their "goodness". According to the AIC and BIC I have chosen the logit model. 

```{r fig 01, fig.width=8,fig.height=3,  echo = FALSE , results = 'asis', warning = FALSE, message = FALSE}
predict_logit
```

# Appendix

```{r fig 1, fig.width=8,fig.height=4,  echo = FALSE , results = 'asis', warning = FALSE, message = FALSE}
ggarrange(p1, p2, p3, p4, nrow = 2, ncol=2 )
```
\begin{center}
Possible variable transformations
\end{center}

```{r fig 3, fig.width=18,fig.height=25,  echo = FALSE , results = 'asis', warning = FALSE, message = FALSE }
ggarrange(p_age,
          p_male, 
          p_cp, 
          p_trestbps,
          p_chol,
          p_restecg, 
          p_thalach, 
          p_exang, 
          p_oldpeak,
          p_slope, 
          p_ca, 
          p_thal,
          nrow = 7, ncol = 2 )
```

\begin{center}
```{r, results = 'asis', echo = FALSE, scalebox = 0.5}
texreg(list(lpm1, lpm2, lpm), table = FALSE, use.packages = FALSE, center = TRUE, omit.coef = "as.factor*", 
       custom.model.names = c("LPM model 1", "LPM model 2", "LPM model 3"),
       custom.coef.names = c("Intercept", "Gender", "Age below 52", "Age between 52 and 61", "Age above 61", 
                             "Resting blood pressure under 115", "Resting blood pressure between 115 and 130",
                             "Resting blood pressure above 130", "Serum cholesterol under 210",
                             "Serum cholesterol between 210 and 270", "Serum cholesterol between 270 and 430",
                             "Serum cholesterol above 430", "Fasting blood sugar above 120 mg/dl",
                             "Maximum heart rate achieved below 140", "Maximum heart rate achieved above 140",
                             "Exercise-induced angina occured", "Oldpeak below 4", "Oldpeak above 4",
                             "Number of major vessels")) 
```

Comparing LPM models with different number of variables (quantitative variables are hidden from the third model to fit onto one page but I am controlling the model on them as well)
\end{center}

\begin{center}
```{r, results = 'asis', echo = FALSE, scalebox = 0.5}
texreg(list(lpm, logit, logit_marg, probit, probit_marg), table = FALSE, use.packages = FALSE, center = TRUE, omit.coef = "as.factor*", 
       custom.model.names = c("LPM", "Logit", "Logit margins", "Probit", "Probit margins"),
       custom.coef.names = c("Intercept", "Gender", "Age below 52", "Age between 52 and 61", "Age above 61", 
                             "Resting blood pressure under 115", "Resting blood pressure between 115 and 130",
                             "Resting blood pressure above 130", "Serum cholesterol under 210",
                             "Serum cholesterol between 210 and 270", "Serum cholesterol between 270 and 430",
                             "Serum cholesterol above 430", "Fasting blood sugar above 120 mg/dl",
                             "Maximum heart rate achieved below 140", "Maximum heart rate achieved above 140",
                             "Exercise-induced angina occured", "Oldpeak below 4", "Oldpeak above 4",
                             "Number of major vessels")) 
```

Comparing LPM model with Logit and Probit models (quantitative variables are hidden from the third model to fit onto one page but I am controlling the model on them as well)
\end{center}